Cognitive Context: Impact on the Perception of a Robot

### 2015-07-02 main.tex
Minor tuning

\rightheader{Cognitive Context: Impace on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Cognitive Context: Impact on the Perception of a Robot}

@@

\paragraph{Participants}

@@

$ \frac{\sum_{AOI=1}^{N}\left | \frac{Time_{Human}^{i}}{Area_{Human}^{i}} - \frac{Time_{Robot}^{i}}{Area_{Robot}^{i}} \right |}{N}$

@@

To compare gazing behaviours across conditions, we compute a \emph{difference of
of gaze pattern} as...

\fxfatal{put here the formula + explanations}

@@

\begin{figure}
    \centering
    \includegraphics[width=10cm]{ManipulationCheck}
    \caption{Average ratings for the manipulation check question}
    \label{fig:ManipulationCheck}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}
    \caption{Difference in gaze patterns \vs \anti}
    \label{h2}
\end{figure}

>>>>

\rightheader{Cognitive Context: Impact on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Cognitive Context: Impact on the Perception of a Robot}

@@

Figure~\ref{course_of_study} gives an overview of the protocol, detailed
hereafter.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.3\linewidth]{experimentFlow}
    \caption{Overview of the course of the study}
    \label{course_of_study}
\end{figure}
\paragraph{Participants}

@@

@@

To compare gazing behaviours across conditions, we compute a \emph{difference in
gaze patterns} over the $N(=10)$ AOIs:

{\large
\[
    \delta_{\mathcal{H}, \mathcal{R}}^{\text{gaze}} =
    \frac{\sum\limits_{{\text{{\sc aoi}s}}}\left |
    \frac{\text{Time}_{\text{Human}}^{\text{\sc
aoi}}}{\text{Area}_{\text{Human}}^{\text{\sc aoi}}} -
\frac{\text{Time}_{\text{Robot}}^{\text{\sc
aoi}}}{\text{Area}_{\text{Robot}}^{\text{\sc aoi}}} \right |}{N}
\]
}

\emph{Time} and \emph{Area} are normalized, respectively for the total
video length and the total area of the AOIs.

@@

\begin{figure}
    \centering
    \includegraphics[width=7cm]{ManipulationCheck}
    \caption{Average ratings for the manipulation check question}
    \label{fig:ManipulationCheck}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}
    \caption{Difference in gaze patterns $\delta_{\mathcal{H},
    \mathcal{R}}^{\text{gaze}}$ \vs \anti}
    \label{h2}
\end{figure}
